Abstract Plots

### 2021-08-19 Abstract.Rmd
Adding set seed for reproducibility

```{r}
set.seed()
#Create Signature 4 Sample
sig4.500 <- create_signature_sample_vector(signature.4.mat, 500)
sig4.profile <- vector_to_matrix(sig4.500)

>>>>

```{r}
set.seed(500)
#Create Signature 4 Sample
sig4.500 <- create_signature_sample_vector(signature.4.mat, 500)
sig4.profile <- vector_to_matrix(sig4.500)
